Fourmile Calibrations and Output

### 2025-03-20 fourmile_output_dec2024.Rmd
updated pbias fig so scale is centered on 0

>>>>

### #### test
# Compute max absolute value for symmetric limits
max_abs <- max(abs(flow_plot_updated$pbias), na.rm = TRUE)

both_pbias_plot <- flow_plot_updated %>%
  ggplot(aes(x = year_excluded, 
             y = year, 
             fill = pbias)) +
  geom_tile(color = "white") +
  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
  paletteer::scale_fill_paletteer_c(
    "grDevices::Green-Brown",
    limits = c(-max_abs, max_abs),
    oob = scales::squish
  ) +
  geom_text(aes(label = sprintf("%.2f", pbias)), 
            color = "black", 
            size = 2.75) +
  theme_bw(base_size=18) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = 'bottom',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(2, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
    legend.margin = margin(t = -8, b = -4, unit = "pt")
  ) +
  labs(y = "Year",
       x = 'Year excluded',
       fill = 'Pbias')

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_basic_0center.png',
       dpi=600,
       width = 10,
       height = 6)
